Reproducible Workflow on a Public Cloud for Computational Fluid Dynamics

### 2019-04-11 tex/MesnardoBarba2019.tex
Minor edits (see list)
* Add "drop cap" letters.
* Mention Linux VMs for IB on NC-series.
* Drop "front" and "back" boundaries.
* Change "Lessons Learned" to "User Experience".
* Add comment about paragraph to add (university cost model).

Reproducible research and replication studies are essential components for the progress of evidence-based science, even more now when nearly all fields advance via computation.
We use computer simulations and data models to create new knowledge,
but how do we provide evidence that this new knowledge is justified? 
Traditional journal publications exclude software and data products from the peer-review process, yet reliance on ever more complex computational artifacts and methods is the norm.
Lacking standards for documenting, reporting and reviewing the computational facets of research, it becomes difficult to verify and corroborate the findings presented in journals and conferences \cite{donoho_et_al_2009}.

@@

The top concerns of researchers considering cloud computing are performance and cost. 
Until just a few years ago, the products offered by cloud providers were unsuitable to the needs of computational scientists using HPC, due to performance overhead of virtualization and lack of support for fast networking. 
Azure only introduced nodes with GPU devices during late 2016 and Infiniband support for the NC-series in 2017.
Our first objective was to assess performance on cloud nodes for the type of computations in our research workflows with  tightly coupled parallel applications. 
We present results from benchmarks and test-cases showing that we are able to obtain similar performance in terms of latency and bandwidth using the Azure virtual network, comparing to a traditional university-managed HPC cluster (Colonial One).
Table \ref{tab:hw_specs} lists the hardware specifications of the nodes used on Microsoft Azure and Colonial One.
Our target research application relies on three-dimensional CFD simulations with our in-house research software. We include here a sample of the types of results needed to answer our research question, obtained by running on the public cloud using the reproducible workflow described in Section \ref{sec:workflow}.
The goal is to showcase the potential of cloud computing for CFD, share the lessons we learned in the process, as well as analyze the cost scenarios for full applications.

@@

Although the two-dimensional simulations can give us some insights into to flow dynamics happening in the wake behind the snake, we know that at this Reynolds number ($Re = 2000$), three-dimensional structures will develop in the wake.
We submitted jobs on Azure Batch to perform direct numerical simulation of the three-dimensional flow around a snake model: a cylinder with the an anatomically accurate cross-section.
The computational domain is extended in the $z$-direction over a length of $3.2c$ and the grid now contains about $46$ million cells (with a uniform discretization in the $z$-direction; see Table \ref{tab:grid_specs}).
The grid is kept uniform in the $z$-direction and we enforce periodic conditions at the front and back boundaries.
The simulation ran in a Docker container on Azure Batch using Batch Shipyard.
The job was submitted to a pool of two \texttt{NC24r} nodes using $24$ MPI processes and $4$ GPU devices per node.
The task completed $100,000$ time steps ($100$ time units with a time-step size $\Delta t = 0.01 c / U_\infty$) in about $5$ days and $16$ hours.

@@

\section{Cost Analysis and Lessons Learned}\label{sec:cost}

@@

@@

In a renewed effort to make our research transparent and reproducible by others, we maintain in a public version-controlled repository all the files necessary to re-run the examples highlighted in this paper.
The repository is found at \url{https://github.com/barbagroup/cloud-repro}.

>>>>

\IEEEPARstart{R}{eproducible} research and replication studies are essential components for the progress of evidence-based science, even more now when nearly all fields advance via computation.
We use computer simulations and data models to create new knowledge,
but how do we provide evidence that this new knowledge is justified? 
Traditional journal publications exclude software and data products from the peer-review process, yet reliance on ever more complex computational artifacts and methods is the norm.
Lacking standards for documenting, reporting and reviewing the computational facets of research, it becomes difficult to verify and corroborate the findings presented in journals and conferences \cite{donoho_et_al_2009}.

@@

The top concerns of researchers considering cloud computing are performance and cost. 
Until just a few years ago, the products offered by cloud providers were unsuitable to the needs of computational scientists using HPC, due to performance overhead of virtualization and lack of support for fast networking. 
Azure only introduced nodes with GPU devices during late 2016 and Infiniband support for Linux virtual machines on the NC-series in 2017.
Our first objective was to assess performance on cloud nodes for the type of computations in our research workflows with  tightly coupled parallel applications. 
We present results from benchmarks and test-cases showing that we are able to obtain similar performance in terms of latency and bandwidth using the Azure virtual network, comparing to a traditional university-managed HPC cluster (Colonial One).
Table \ref{tab:hw_specs} lists the hardware specifications of the nodes used on Microsoft Azure and Colonial One.
Our target research application relies on three-dimensional CFD simulations with our in-house research software. We include here a sample of the types of results needed to answer our research question, obtained by running on the public cloud using the reproducible workflow described in Section \ref{sec:workflow}.
The goal is to showcase the potential of cloud computing for CFD, share the lessons we learned in the process, as well as analyze the cost scenarios for full applications.

@@

Although the two-dimensional simulations can give us some insights into to flow dynamics happening in the wake behind the snake, we know that at this Reynolds number ($Re = 2000$), three-dimensional structures will develop in the wake.
We submitted jobs on Azure Batch to perform direct numerical simulation of the three-dimensional flow around a snake model: a cylinder with the an anatomically accurate cross-section.
The computational domain is extended in the $z$-direction over a length of $3.2c$ and the grid now contains about $46$ million cells (with a uniform discretization in the $z$-direction; see Table \ref{tab:grid_specs}).
The grid is kept uniform in the $z$-direction with periodic boundary conditions.
The simulation ran in a Docker container on Azure Batch using Batch Shipyard.
The job was submitted to a pool of two \texttt{NC24r} nodes using $24$ MPI processes and $4$ GPU devices per node.
The task completed $100,000$ time steps ($100$ time units with a time-step size $\Delta t = 0.01 c / U_\infty$) in about $5$ days and $16$ hours.

@@

\section{Cost Analysis and User Experience}\label{sec:cost}

@@

% Discuss cheaper options and university cost models (F&A).

@@

\bigskip
\IEEEPARstart{I}{n} a renewed effort to make our research transparent and reproducible by others, we maintain in a public version-controlled repository all the files necessary to re-run the examples highlighted in this paper.
The repository is found at \url{https://github.com/barbagroup/cloud-repro}.
